\documentclass[12pt]{article}

\usepackage{latexsym,amssymb,amsthm,amsmath,amscd,multirow,marvosym,fixltx2e,tikzsymbols}

\usepackage{tikz,latexsym,amssymb,amsthm,amsmath,amscd,multirow,marvosym,mathrsfs,fixltx2e}
\usetikzlibrary{svg.path}


\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{0cm}
\setlength{\textwidth}{6.5in}
\setlength{\headheight}{-.5 in}
\setlength{\topmargin}{0in}
\setlength{\textheight}{9 in}



\begin{document}

\begin{center} 
  CSC 395 Spring 2017 \\
  Project Proposal\\
  by Conner Gregorich-Trevor, Nick Roberson, and Reilly Noonan Grant\\
  Due: April 17th \\

----------------------------------------------------------------------------------------------------------------------- \end{center}

\begin{enumerate}
  \item[Purpose] 

    Our visualization will be a display of stock data for a company
    overlaid with data relating to how often that company is mentioned
    in social media, or searched for on the internet. We plan to let
    users look over various time frames, and highlight when either the
    stock price or mentions increase quickly. Possibly also look at
    popularity in diffrent locations and look at news data for that
    company in specified a time frame. 
    
    Hopefully users will be able to understand better the relationship between
    stocks and social media.
    Potentially they be able to understand which precedes the
    other, and in what types of situations will one come before the
    other.  When social media comes first, what effect does it have?
    Looking at location data, we predict that where it is trending
    won't matter in terms of how it will effect the stock price.

    We predict that when stock plumets that social
    media will subsequently will increase, and that when stock price
    drastically increases, social media mentions will also
    increase. 

    The amount of data involved in this question makes understanding
    what is going on harder without a visualization. By providing a
    visualization with which someone can examine multiple data sets
    simultaneously we will be able to get a better sense for
    where to direct future questions, and what the general predictions
    we can draw are.
    
  \item[Design]
    
    Our visualization will include a plot with an x-axis of time and
    two y-axes. One y-axis will be stock values, and the other will be
    the social media metric from 0 to 100. Using this plot
    we will graph changes in stock prices over time and changes in the
    social media metric.

    To the left of this we will have a checklist of different keyword
    and stock combinations to choose from.

    Just beneath the plot, we will have a slider which controls the
    time period to display data in. Below that,
    we will include a world map, where darker shaded areas signifiy
    places where the selected keyword is historically more talked
    about in the country.

  \item[Techniques]

    We will be using Google trends data, and Yahoo'spast stock data. We also will investigate using redit, facebook
    twitter and new york times data, but we currently only have access to the Google
    trends, and Yahoo data.

\end{enumerate}
\end{document}